Security Audit of Safeplug

### 2014-02-11 report/design.tex
made minor edits

\subsection{Hardware}
We opened up the Safeplug device to look at the internals.  Figure~\ref{fig:top} shows the top of the board and Figure~\ref{fig:bottom} shows the bottom.  The board incorporates: (A) an SD card slot, (B) a power connector, (C) a USB slot, (D) an ethernet connector, (E) ??, (F) ??, (G) an integrated circuit, and (H), (I) flash memory.

@@

\subsection{Software}
\label{software}
We determined the software on the device from analyzing network traffic logs of the activation process (as described below) and accessing the device via SSH (as described in Section~\ref{sec:SSH}).

@@

Analysis of the TCP dump showed that the Safeplug box repeatedly queried the local DNS server for two items: \url{pogoplug.com} and the NIST standardized time.  The first query for the time was to \url{www.nist.gov}, and subsequent queries included \url{nist1-chi.ustiming.org}, \url{nist1-ny.ustiming.org}, \url{time-nw.nist.gov}, and \url{nist1.symmetricom.com}.  Queries about pogoplug were mostly for \url{service.pogoplug.com} but after that set was tried \url{secure.pogoplug.com} was attempted once.  While it was only connected to the local network, we also did a scan of all the ports of the Safeplug and only port 80 was open.

\subsubsection{Activation and Update Traffic}
\label{updatetraf}
After establishing the initial update behavior, we connected the other end of our homemade router back to the internet and captured traffic on both the network interfaces. As we had seen previously, the first effort of the Safeplug was to query for \url{service.pogoplug.com} and connect, and the send a POST/XML request to that server containing a 16 byte numerical string of type \verb!nid!, \verb!0x0! as \verb!flags!, and a field called \verb!pingdata! with length of 423 bytes and undiscernable contents.  In future work, we hope to explore the contents of this automatic connection with the Pogoplug servers to discover what information is being passed along.

The client computer then navigated to the Pogoplug website to complete the activation processes.  Each step of the process resulted in both TCP and UDP traffic between the Safeplug box and the pogoplug servers.  Most interesting was the update step in which the Safeplug box knew to request a script from \url{<update server IP>/svc/upgrade/safeplug\_switch.sh}.  Since this operation occured over normal HTTP, we were able to use \verb!curl! to recover the same script and examine it to discover the contents of the upgrade.

The upgrade script shows (and the network traffic confirms) that the box downloads and installs the following \verb!.tgz! files: 
\begin{fileName}
safeplug_lighttpd, safeplug_lighttpd_config, safeplug_wget, safeplug_certs, safeplug_gohelper, safeplug_tor, safeplug_tor_config, safeplug_privoxy, safeplug_privoxy_config
\end{fileName}
  Each file is compared to an MD5 hash before being unzipped and installed.  Details about the software found on the Safeplug are discussed in Section \ref{software}.  After the two lighttpd installations, a process called \verb!hbplug! is killed and lighttpd is started.  After the certs are downloaded, the current \verb!/usr/local/ssl! is overwritten with the new certs.  The \verb!go\_helper! is added to the \verb!/opt/xce/sbin! folder, and contains binary files with names related to update and upgrade (which we hope to decompile in future work).

After completing the installations, a default Safeplug configuation file is written with use of Tor set to 1.  (More information about the configuration in Section \ref{spconfig}.)  Finally, the old \verb!rcS! file in \verb!/etc/init.d! is replaced with commands to start lighttpd, tor and privoxy, and the LED on the front of the device is set to green after the completion of the upgrade. This means that the green LED indicates an up-to-date, internet-connected Safeplug, rather than anything about the use of TOR.

\subsubsection{Traffic After Activation}
After the activation and the configuration of the Safeplug as a proxy, all traffic was through the Tor network.  The Safeplug connected to a directory to learn about different relays and seemed to cycle through a small set around the world for different connections.  This demonstrates that Tor is working as expected.  If there is any ``phone-home'' being done by the device after Tor has been turned on, then it is doing so through the Tor network.

\subsubsection{Software on the Safeplug}
As would be suspected from the analysis of the update script described above in Section \ref{updatetraf}, the installed software is in \verb!/opt/xce! and includes lighttpd, privoxy, and tor.  Lighttpd is an open-source webserver, which is serving the settings page on the device - the project's description mentions ``security, speed, compliance, and flexibility [... while being] designed and optimized for high perfomance environments'' \cite{lighttpd}.  Privoxy is a ``non-caching web proxy with advanced filtering capabilities for enhancing privacy, modifying webpage data and HTTP headers, controlling access, and removnig ads and other obnoxious Internet junk'' and it specifically advertises its ``flexible configuration'' \cite{privoxy}.  Privoxy is also open source.  All three pieces of software appear to be there with default configuration files (with all appropriate citations and comments present).  The fourth piece of software discovered on the device, which does not seem to be installed during the activation process is the Dropbear SSH server and client, used to support SSH access to the device \cite{dropbear}.  The Safeplug uses its own configuration files to determine how these pieces of software are set up and used.

\subsubsection{Configuration on the Safeplug}
\label{spconfig}
The Safeplug configuration files can be found in \verb!/opt/xce/etc! and include \verb!sp.conf! and \verb!sp_version! and \verb!sp_torexceptions!.  The first contains all of the important details from the configuration page (whether to use Tor, whether to be a relay, whether to adblock) as well as a hidden option about whether to be an exitrelay for the Tor network.  This is not documented anywhere on the site, so enabling this option would likely require SSH access to discover it, thereby breaking the warranty, but it is interesting that this option is available.  The version file is likely used for updates, and the exceptions file is used by the privoxy configuation to control the whitelist of sites not to connect to via Tor.

These configuration files are read by the scripts in \verb!/opt/xce/etc/init.d! which enable lighttpd, privoxy, and tor.  As expected, Privoxy looks at the Tor, adblock and exceptions configurations, and Tor reads the \verb!sp.conf! file to set which Tor configuration file (regular, relay or exitrelay) to use.

>>>>

\subsection{Hardware}
Before investigating the software, we took apart one of the two Safeplug devices we purchased in order to see the physical components.  Figure~\ref{fig:top} shows the top of the board and Figure~\ref{fig:bottom} shows the bottom.  The board incorporates: (A) an SD card slot, (B) a power connector, (C) a USB slot, (D) an ethernet connector, (E) ethernet transceiver, (F) lan transformer, (G) an integrated circuit, and (H), (I) flash memory.

@@

\subsection{Software}
\label{software}
We determined the software on the device from analyzing network traffic logs of the activation process and accessing the device via SSH.

@@

Analysis of the TCP dump showed that the Safeplug box repeatedly queried the local DNS server for two items: the NIST standardized time and \url{pogoplug.com}.  The first query for the time was to \url{www.nist.gov}, and subsequent queries included \url{nist1-chi.ustiming.org}, \url{nist1-ny.ustiming.org}, \url{time-nw.nist.gov}, and \url{nist1.symmetricom.com}.  Queries about pogoplug were mostly for \url{service.pogoplug.com}, but \url{secure.pogoplug.com} was attempted once.  While it was connected to the local network, we also did a scan of all the ports of the Safeplug and only port 80 was open.

\subsubsection{Activation and Update Traffic}
\label{updatetraf}
After establishing the initial update behavior, we connected the other end of our router back to the internet and captured traffic on both of the network interfaces. As we had seen previously, the first effort of the Safeplug was to query for \url{service.pogoplug.com} and connect, and then send a POST/XML request to that server containing a 16 byte numerical string of type \verb!nid!, \verb!0x0! as \verb!flags!, and a field called \verb!pingdata! with length of 423 bytes and undiscernable contents.

The client computer then navigated to the Pogoplug website to complete the activation process.  Each step of the process resulted in both TCP and UDP traffic between the Safeplug box and the Pogoplug servers.  Most interesting was the update step in which the Safeplug box knew to request a script from \url{<update server IP>/svc/upgrade/safeplug\_switch.sh}.  Since this operation occured over normal HTTP, we were able to use \verb!curl! to recover the same script and examine it to discover the contents of the upgrade.

The upgrade script shows (and the network traffic confirms) that the box downloads and installs the following \verb!.tgz! files: 
\begin{fileName}
safeplug_lighttpd, safeplug_lighttpd_config, safeplug_wget, safeplug_certs, safeplug_gohelper, safeplug_tor, safeplug_tor_config, safeplug_privoxy, safeplug_privoxy_config
\end{fileName}
  Each file is compared to an MD5 hash before being unzipped and installed.  Details about the software found on the Safeplug are discussed in Section \ref{software}.  After the safeplug\_lighttpd and safeplug\_lighttpd\_config installations, a process called \verb!hbplug! is killed and lighttpd is started.  After the certs are downloaded, the current \verb!/usr/local/ssl! is overwritten with the new certs.  The \verb!go\_helper! is added to the \verb!/opt/xce/sbin! folder, and contains binary files with names related to update and upgrade.

After completing the installations, a default Safeplug configuation file is written with use of Tor set to 1.  More information about the configuration is in Section \ref{spconfig}.  Finally, the old \verb!rcS! file in \verb!/etc/init.d! is replaced with commands to start lighttpd, tor and privoxy, and the LED on the front of the device is set to green after the completion of the upgrade. This means that the green LED indicates an up-to-date, internet-connected Safeplug, rather than anything about the use of TOR.

\subsubsection{Traffic After Activation}
After the activation and the configuration of the Safeplug as a proxy, all traffic runs through the Tor network.  The Safeplug connected to a directory to learn about different relays and seemed to cycle through a small set around the world for different connections.  This demonstrates that Tor is working as expected.  If there is any ``phone-home'' being done by the device after Tor has been turned on, then it is doing so through the Tor network.

\subsubsection{Software on the Safeplug}
As would be suspected from the analysis of the update script described above in Section \ref{updatetraf}, the installed software is in \verb!/opt/xce! and includes lighttpd, privoxy, and tor.  Lighttpd is an open-source webserver, which is serving the settings page on the device - the project's description mentions ``security, speed, compliance, and flexibility [... while being] designed and optimized for high perfomance environments'' \cite{lighttpd}.  Privoxy is a ``non-caching web proxy with advanced filtering capabilities for enhancing privacy, modifying webpage data and HTTP headers, controlling access, and removing ads and other obnoxious Internet junk'' and it specifically advertises its ``flexible configuration'' \cite{privoxy}.  Privoxy is also open source.  All three pieces of software appear to have default configuration files.  The fourth piece of software discovered on the device, which does not seem to be installed during the activation process is the Dropbear SSH server and client, used to support SSH access to the device \cite{dropbear}.  The Safeplug uses its own configuration files to determine how these pieces of software are set up and used.

\subsubsection{Configuration on the Safeplug}
\label{spconfig}
The Safeplug configuration files can be found in \verb!/opt/xce/etc! and include \verb!sp.conf! and \verb!sp_version! and \verb!sp_torexceptions!.  The first contains all of the important details from the configuration page (whether to use Tor, whether to be a relay, whether to adblock) as well as a hidden option about whether to be an exit relay for the Tor network.  This is not documented anywhere on the site, so enabling this option would likely require SSH access to discover it, thereby breaking the warranty, but it is interesting that this option is available.  The version file is likely used for updates, and the exceptions file is used by the privoxy configuation to control the whitelist of sites not to connect to via Tor.

These configuration files are read by the scripts in \verb!/opt/xce/etc/init.d! which enable lighttpd, privoxy, and tor.  As expected, Privoxy looks at the Tor, adblock and exceptions configurations, and Tor reads the \verb!sp.conf! file to set which Tor configuration file (regular, relay or exit relay) to use.

### 2014-02-11 report/discussion.tex
made minor edits

\subsection{Engineering Fixes}
The most critical engineering fix is authentication in the POST calls to prevent the cross-site attack.  A typical example is a cookie and a hidden form field set in the Settings page the Safeplug hosts, that must be returned by the browser when making the POST request to the RPC server (CITE).  Although someone doing a cross-site scripting attack such as the one described above could get the cookie sent, if the cookie is set correctly, then the adversary would not be able to examine the contents of the cookie to determine what to put in the form field.

\subsection{Structural Problems}
However, there are much more significant structural problems with implementing a Tor connection via an HTTP proxy.  Several of the usability problems involve user awareness and vigilance.  For example, cookies and fingerprinting problems mean that users could still be tracked across websites, regardless of whether the ad-block functionality on the Safeplug is enabled.  This poses an unreasonable stress on users who must be aware of the their browsing practices and does not bode well for the advertised security and anonymity.

@@

\subsection{Opportunities}
Despite all the structural problems, is there a room or a market for a Torifying piece of hardware?  Given the security pitfalls in comparison to a piece of software such as the Tor browser bundle, there seems to be no reason for a computer that can run the Tor browser bundle to purchase the Safeplug or any other device.  For mobile phones, the proxy problems with mobility contribute to an already high usability cost.  However, there are an emerging classes of ``smart home'' devices which may connect to the internet.  It is possible that some of these devices can be configured to use an HTTP proxy or some other middle box to Torify their traffic to an external service provider.  For them, is the benefit of some anonymity via a Safeplug-like device worthwhile?  Since the data sent by these devices to the service provider likely contains lots of identifying information, the use of Tor probably only protects the user's location at the expense of connection time and load on the Tor network.  Since proxy configuration on such devices is likely to be difficult and the amount of information hidden is unlikely to be worth the effort, a Torifying box that functions as a proxy has questionable use in this space as well.

>>>>

\subsection{Engineering Fixes}
The most critical engineering fix is authentication in the POST calls to prevent the cross-site request forgery attack.  A typical example is a cookie and a hidden form field set in the Settings page the Safeplug hosts; the cookie must be returned by the browser when making the POST request to the RPC server (CITE).  Although someone doing a cross-site request forgery attack such as the one described above could get the cookie sent, if the cookie is set correctly, then the adversary would not be able to examine the contents of the cookie to determine what to put in the form field.

\subsection{Structural Problems}
However, there are much more significant structural problems with implementing a Tor connection via an HTTP proxy.  Several of the usability problems involve user awareness and vigilance.  For example, cookies and fingerprinting problems mean that users could still be tracked across websites, regardless of whether the ad-block functionality on the Safeplug is enabled.  This poses an unreasonable stress on users who must be aware of their browsing practices and does not bode well for the advertised security and anonymity.

@@

\subsection{Opportunities}
Despite all the structural problems, is there a market for a Torifying piece of hardware?  Given the security pitfalls in comparison to a piece of software such as the Tor browser bundle, there seems to be no reason for a user that can run the Tor browser bundle to purchase the Safeplug or any other device.  For mobile phones, the proxy problems with mobility contribute to an already high usability cost.  However, there are an emerging class of ``smart home'' devices which may connect to the internet.  It is possible that some of these devices can be configured to use an HTTP proxy or some other middle box to Torify their traffic to an external service provider.  For them, is the benefit of some anonymity via a Safeplug-like device worthwhile?  Since the data sent by these devices to the service provider likely contains lots of identifying information, the use of Tor probably only protects the user's location at the expense of connection time and load on the Tor network.  Since proxy configuration on such devices is likely to be difficult and the amount of information hidden is unlikely to be worth the effort, a Torifying box that functions as a proxy has questionable use in this space as well.

### 2014-02-11 report/implementattacks.tex
made minor edits

This attacker could also be any kind of device on the local network, or the local gateway if it is compromised.  The NSA ``Spymall'' catalog leaked in December shows tools for compromising a number of different devices and home routers are traditionally insecure \cite{spymall}.  It is easy to imagine any malicious party, not just one with the resources of a government, (although governments might be some of the most interested parties in attacking a Tor proxy) compromising the gateway and using that access make a disabling RPC call into the Safeplug.  This would occur silently from the perspective of a client unless the happen to check the Settings page for the Safeplug.  Instead, the client would continue browsing with a belief that they are protected by their use of the Tor network, while in fact any external adversary can track their traffic.

@@

\begin{enumerate}
\item Set up a web page with the crafted Javascript code, which will send a POST request of the following format to all addresses in the range: \url{http://<IP address>/svc/xspctrl/disableTor} (See Appendix \ref{App:AppendixA}).
\item Send the malicious link to a user in the targeted private network.
\item Once the user clicks the link and loads the malicious site, the correctly formatted POST request will be sent to every IP address in the ranges.  
\item Tor is disabled silently.  The user must check or refresh her settings page to learn that Tor is turned off.  
\end{enumerate}

This exploits the RPC server in the same manner that the Insider Attack does.  While this attack requires a greater amount of time because the local IP address of the Safeplug must be guessed via search, but the number of private address spaces is small, and the space likely to be occupied by a Safeplug on a home network is even smaller.

The largest observed time to send requests to the 192.168.0.0/24 space was ~400 milliseconds; the entire attack costs ~800 milliseconds for sending request to both 192.168.0.0/24 and 192.168.1.0/24 ranges - even when the website was being loaded over Tor.  In the case of a private network in the range of 172.16.0.0/16, the attack took less than ~12 minutes (this generates script timeout warnings in most major browsers, which affects the timing of this attack).  This means that it would take a few hours to send requests to the full 172.16.0.0/12 range, which is commonly used in business networks.  The final private network space is 10.0.0.0/8 which is too large for an exhaustive search, but some simple optimization might make it feasible as well.  For example, using a GET request to get and parse the Safeplug settings page would allow the script to positively identify the safeplug and stop the search.  However, the 192.168.0.0/24 and 192.168.1.0/24 ranges are much more common in home networks; because Safeplug is geared towards home network use, in most cases the script will take less than a second, a trivial amount of time for the attacker to spend.

In addition to disabling Tor, the attacker can modify any other settings on the device.  This includes: enabling/disabling Tor, enabling/disabling ad-blocking, enabling/disabling the use of the device as a Tor relay node [note: this requires the user to do additional setup], enabling/disabling the use of the device as an exit node (if it is already a relay).  Lastly, the attacker can also modify the user's whitelist of sites that should not be routed through Tor.  This whitelist attack is particularly dangerous because the change is silent and much harder for the user to notice the addition of a single website to the whitelist than a global loss of Tor.  (Removal of a webpage from the whitelist is likely to to cause usability problems and be more evident.)

\subsection{Gaining Access through SSH}
\label{sec:SSH}
    \subsubsection{Accessing the Device}
    Safeplug runs an RPC server that allows the enabling of SSH access via HTTP. SSH instructions for Cloud Engine's other device (Pogoplug) are widely available online and an email in the Tor-talk mailing list confirms that the instructions are the same (although the Pogoplug support staff note that SSH access breaks the warranty!) \cite{ceadmin}:
\begin{fileName}
curl --data ``'' http://<IP-of-Safeplug>/svc/xspctrl/enableSSHD
ssh root@<IP-of-Safeplug>
password: ceadmin
\end{fileName}

>>>>

This attacker could also be any kind of device on the local network, or the local gateway if it is compromised.  The NSA ``Spymall'' catalog leaked in December shows tools for compromising a number of different devices and home routers are traditionally insecure \cite{spymall}.  It is easy to imagine any malicious party, not just one with the resources of a government, (although governments might be some of the most interested parties in attacking a Tor proxy) compromising the gateway and using that access to make a disabling RPC call into the Safeplug.  This would occur silently from the perspective of a client unless they happen to check the Settings page for the Safeplug.  Instead, the client would continue browsing with a belief that they are protected by their use of the Tor network, while in fact any external adversary can track their traffic.

@@

\begin{enumerate}
\item Set up a web page with the crafted Javascript code, which will send the POST request of the following format to all addresses in the common ranges: \url{http://<IP address>/svc/xspctrl/disableTor} (See Appendix \ref{App:AppendixA}).
\item Send the malicious link to a user in the targeted private network.
\item Once the user clicks the link and loads the malicious site, the correctly formatted POST request will be sent to every IP address in the ranges.  
\item Tor is disabled silently.  The user must check or refresh her settings page to learn that Tor is turned off.  
\end{enumerate}

This exploits the RPC server in the same manner that the Insider Attack does.  While this attack requires a greater amount of time because the local IP address of the Safeplug must be guessed via search, the number of private address spaces is small, and the space likely to be occupied by a Safeplug on a home network is even smaller.

The largest observed time to send requests to the 192.168.0.0/24 space was approximately 400 milliseconds; the entire attack costs approximately 800 milliseconds for sending request to both 192.168.0.0/24 and 192.168.1.0/24 ranges - even when the website was being loaded over Tor.  In the case of a private network in the range of 172.16.0.0/16, the attack took less than ~12 minutes (this generates script timeout warnings in most major browsers, which affects the timing of this attack).  This means that it would take a few hours to send requests to the full 172.16.0.0/12 range, which is commonly used in business networks.  The final private network space is 10.0.0.0/8 which is too large for an exhaustive search, but some simple optimization might make it feasible as well.  For example, using a GET request to get and parse the Safeplug settings page would allow the script to positively identify the safeplug and stop the search.  However, the 192.168.0.0/24 and 192.168.1.0/24 ranges are much more common in home networks; because Safeplug is geared towards home network use, in most cases the script will take less than a second, a trivial amount of time for the attacker to spend.

In addition to disabling Tor, the attacker can modify any other settings on the device.  This includes: enabling/disabling Tor, enabling/disabling ad-blocking, enabling/disabling the use of the device as a Tor relay node [note: this requires the user to do additional setup], enabling/disabling the use of the device as an exit node (if it is already a relay).  Lastly, the attacker can also modify the user's whitelist of sites that should not be routed through Tor.  This whitelist attack is particularly dangerous because the change is silent and much harder for the user to notice the addition of a single website to the whitelist than a global loss of Tor.  (Removal of a webpage from the whitelist is likely to cause usability problems and be more evident.)

\subsection{Gaining Access through SSH}
\label{sec:SSH}
    Safeplug runs an RPC server that allows the enabling of SSH access via HTTP. SSH instructions for Cloud Engine's other device (Pogoplug) are widely available online and an email in the Tor-talk mailing list confirms that the instructions are the same \cite{ceadmin}:
\begin{fileName}
curl --data ``'' http://<IP-of-Safeplug>/svc/xspctrl/enableSSHD
ssh root@<IP-of-Safeplug>
password: ceadmin
\end{fileName}

### 2014-02-11 report/related.tex
made minor edits

To our knowledge, there has been no other study analyzing the security of Pogoplug's Safeplug device.  However there has been much prior research on the primary technology that the device uses: Tor.  Additionally, the security goals that Safeplug attempts to achieve have been previously studied in great detail; these include fingerprinting and cookies.

@@

{\bf Fingerprinting.}  Website fingerprinting attacks as well as remote physical device fingerprinting attacks have shown they can identify users, even when specific defense have been used in order to prevent these attacks. Previous research has shown that web page fingerprinting attacks are possible~\cite{dyer, herrmann, panchenko}.  Cai, Zhang, Joshi, and Johnson introduced both a web page and website fingerprinting attack that defeats many recently proposed defenses, including cover traffic and randomized pipeling.  They find that their attack is successful 83.7\% of the time when the defense is the use of Tor; the success rate decreases to 52.2\% when the defense is the use of Tor, randomized pipelining, padding packets to 1500 bytes, and adding cover traffic at a 1:1 ratio~\cite{fingerprint1}.  These results can be extended to the security of Safeplug.  Because Safeplug uses only Tor to anonymize users, it may be susceptible to this fingerprinting attack.

>>>>

To our knowledge, there has been no other study analyzing the security of Pogoplug's Safeplug device.  However there has been much prior research on the primary technology that the device uses: Tor.  Additionally, the security vulnerabilities that Safeplug attempts to secure users against have been previously studied in great detail; these include fingerprinting and cookies.

@@

{\bf Fingerprinting.}  Website fingerprinting attacks as well as remote physical device fingerprinting attacks have shown they can identify users, even when specific defenses have been used in order to prevent these attacks. Previous research has shown that web page fingerprinting attacks are possible~\cite{dyer, herrmann, panchenko}.  Cai, Zhang, Joshi, and Johnson introduced both a web page and website fingerprinting attack that defeats many recently proposed defenses, including cover traffic and randomized pipeling.  They find that their attack is successful 83.7\% of the time when the defense is the use of Tor; the success rate decreases to 52.2\% when the defense is the use of Tor, randomized pipelining, padding packets to 1500 bytes, and adding cover traffic at a 1:1 ratio~\cite{fingerprint1}.  These results can be extended to the security of Safeplug.  Because Safeplug uses only Tor to anonymize users, it may be susceptible to this type of fingerprinting attack.

### 2014-02-11 report/usability.tex
made minor edits

Before setting up and using the Safeplug device, we read a variety of news articles as well as opinions through the Tor mailing list~\cite{tormailinglist}.  There were many thoughts on the Terms of Service and the option to use the device as a Tor relay node; this inspired us to start our analysis with these items.

\subsection{Terms of Service}
\label{tos}
Safeplug's Terms of Service are interesting because they are controlling, yet the product they are for is a device for anonymization.  The first section of the Terms of Service explains how to agree to them:

@@

Most Safeplug users will likely not read the Terms of Service once, let alone on a regular basis; therefore, most users will be blind to any changes.  It is also interesting that these Terms of Service are only accessible through a small link at the bottom of the Safeplug website \cite{safeplug}; specifically, there is no documentation, including the Terms of Service, in the package that the device was shipped in.  Further along in the Terms of Service, the makers of Safeplug were sloppy when they wrote:

@@

One of our concerns is how understandable this setting is to the average Internet user.  The settings page describes Tor in an extremely basic way, as shown in Figure~\ref{fig:funnydesc}, but describes the functionality of a Tor relay node in a much more technical manner.  This description is shown in Figure~\ref{fig:relaydesc}.  If the majority of users can only understand the simpler description, then they likely won't understand the description of a Tor relay node.  This could be a problem if users simply decide not to do anything with that setting (i.e. don't change the setting to use Safeplug as a relay node).  Then there would be a large increase in use of the Tor network, yet most of the users are not giving back to it.

@@

\subsubsection{Setting up Safeplug} The first step was to plug Safeplug into our router and activate our device.  Our instructions are shown in Figure~\ref{fig:instructions}.  We followed them, activated our device, and then ended on the configuration page.  The configuration page has a combination of platforms and browsers, with a different set of proxy configuration instructions for each one.  It is interesting to note that the only platform options were: OSX, Windows, Android, and iOS.  Figure~\ref{fig:proxyconfig} shows our configuration.

@@

After we finished our configuration, we were taken to our settings.  This page is shown in Figure~\ref{fig:settings}.  This allowed us to turn on/off Tor, add white-listed websites, turn on/off ad-blocking, and turn on/off the ability of our device to be a relay node.

@@

Next, we wanted to see how usable this would be to a normal Internet user.  A user would probably decide not to use Safeplug if they could not read their web pages (if they were not in their native language), or if they could not log into their accounts (some web sites will lock a user out if they try to log in from multiple countries in a short time period).  While browsing the Internet, we experienced some pages in German and Swedish, which is expected with Tor; if a user is not familiar with Tor, then they may just get frustrated and stop using Safeplug altogether.  We were also prompted with the page in Figure~\ref{fig:funnygoogle} when we tried to log into our Google account.

@@

>>>>

Many news articles were published to announce the release of the Safeplug in addition to a lengthy discussion on the Tor-talk mailing list~\cite{tormailinglist}.  There were many thoughts on the Terms of Service and the option to use the device as a Tor relay node; this inspired us to start our analysis with these items.

\subsection{Terms of Service}
\label{tos}
The first section of the Terms of Service explains how to agree to them:

@@

Most Safeplug users will likely not read the Terms of Service once, let alone on a regular basis; therefore, most users will be blind to any changes.  It is also interesting that these Terms of Service are only accessible through a small link at the bottom of the Safeplug website \cite{safeplug}; specifically, there is no documentation, including the Terms of Service, in the package that the device was shipped in.  The Terms of Service next includes:

@@

One of our concerns is how understandable this setting is to the average Internet user.  The settings page describes Tor in an extremely basic way:

\begin{quotation}
``Safeplug uses the Tor network to secure your Internet connection.  Tor works by routing your Internet through a series of random destinations, much like driving a twisty, complicated route to throw off someone who is following you, making it impossible for websites and organizations to identify the source or destination of Internet traffic.'' \cite{safeplug}
\end{quotation}

On the other hand, it describes the functionality of a Tor relay node in a much more technical manner.  This description is shown in Figure~\ref{fig:relaydesc}.  If the majority of users can only understand the simpler description, then they likely won't understand the description of a Tor relay node.  This could be a problem if users simply decide not to do anything with that setting (i.e. don't change the setting to use Safeplug as a relay node).  Then there would be a large increase in use of the Tor network, yet most of the users are not giving back to it.

@@

\subsubsection{Setting up Safeplug} The first step was to plug Safeplug into our router and activate our device.  Our instructions are shown in Figure~\ref{fig:instructions}.  We followed them, activated our device, and then ended on the configurations page.  The configurations page has a combination of platforms and browsers, with a different set of proxy configuration instructions for each one.  It is interesting to note that the only platform options were: OSX, Windows, Android, and iOS.  Figure~\ref{fig:proxyconfig} shows our configuration.

@@

After we finished our configuration, we were taken to our settings page.  This page is shown in Figure~\ref{fig:settings}.  This allowed us to turn Tor on/off, add white-listed websites, turn ad-blocking on/off, and turn the ability of our device to be a relay node on/off.

@@

Next, we wanted to see how usable this would be to a normal Internet user.  A user would probably decide not to use Safeplug if they could not read their web pages (if they were not in their native language), or if they could not log into their accounts (some web sites will lock a user out if they try to log in from multiple countries in a short time period).  While browsing the Internet, we experienced some pages in German and Swedish, which is expected with Tor; if a user is not familiar with Tor, then they may just get frustrated and stop using Safeplug altogether.  We were also prompted with the page in Figure~\ref{fig:funnygoogle} when we tried to log into our Google account, indicating that Google noticed we were trying to login from different locations.

@@

\subsection{Latency}
This is a todo item for Annie.
